global-model (ODE)

### 2015-03-03 documentation/interactive_spexmodel_bifurcations.Rmd
interactive bifurcation diagram (Shiny): refer to simfunctions.r

  ini_rho <- function(rho_1) {
    c(
    rho_1 = rho_1,
    rho_11 = rho_1*rho_1,
    rho_10 = rho_1*(1-rho_1)*2,
    rho_00 = (1-rho_1)*(1-rho_1),
    rho_0 = 1-rho_1
    )

  }

d_rho_1 <- function(rho, parms) { 
  with(parms,
       r * (b + (f - b) * (rho[1] - rho[2])/(1- rho[1]) ) * rho[1]^( 1 + alpha) * (1 - rho[1]/(K * (1-c*(rho[1] - rho[2])/(1- rho[1])) ) ) - m * rho[1] - ( (a + v*rho[2]/rho[1]) * rho[1]^( 1 + q) * L)/(1 +(a + v*rho[2]/rho[1]) * (h / (1- p * rho[2]/rho[1]) ) * rho[1]^( 1 + q)) 
       )  
  }

d_rho_11 <- function(rho,  parms) { 
  with(parms,
       2* (rho[1] - rho[2]) * r * (b + (f - b) * (rho[1] - rho[2])/(1- rho[1]) ) * rho[1]^( 1 + alpha) * (1 - rho[1]/(K * (1-c*(rho[1] - rho[2])/(1- rho[1])) ) ) / (1-rho[1]) - 2 * rho[2] * m  - 2 * rho[2] * ( (a + v*rho[2]/rho[1]) * rho[1]^( 1 + q) * L)/(1 +(a + v*rho[2]/rho[1]) * (h / (1- p * rho[2]/rho[1]) ) * rho[1]^( 1 + q)) 
       )  
  }

odesys_spex <- function(t, rho, parms = model_parms) {
  rho_1 <- d_rho_1(rho, parms)
  rho_11 <- d_rho_11(rho, parms)
  list(c(rho_1, rho_11, rho_1-rho_11, 1-rho_1-(rho_1-rho_11),1-rho_1  
               ) )
}

@@

inputPanel(
  sliderInput("r", label = "max. growth rate:",
              min = 0.0, max = 3, value = 1, step = 0.01),
  sliderInput("b", label = "environmental quality:",
              min = 0.0, max = 1, value = 0.1, step = 0.01),
  sliderInput("K", label = "carrying capacity:",
              min = 0.0, max = 1, value = 0.9, step = 0.01),
  sliderInput("alpha", label = "water runoff:",
              min = 0.0, max = 1, value = 0, step = 0.01),
  sliderInput("f", label = "local facilitation:",
              min = 0.0, max = 1, value = 0.9, step = 0.01),
  sliderInput("c", label = "local competition:",
              min = 0.0, max = 1, value = 0.1, step = 0.01)
)

@@

inputPanel(
  sliderInput("m", label = "intrinsic mortality:",
              min = 0.0, max = 1, value = 0.05, step = 0.01),
  sliderInput("a", label = "search efficiency:",
              min = 0.0, max = 1, value = 0.6, step = 0.01), 
  sliderInput("h", label = "handling time:",
              min = 0.0, max = 200, value = 50, step = 1), 
  sliderInput("L", label = "livestock units:",
              min = 0.0, max = 100, value = 6, step = 1),
  sliderInput("q", label = "hill coefficient:",
              min = 0.0, max = 1, value = 0, step = 0.01),
  sliderInput("v", label = "local attractivity:",
              min = 0.0, max = 1, value = 0.0, step = 0.01),
  sliderInput("p", label = "local protection:",
              min = 0.0, max = 1, value = 0.8, step = 0.01)
)

@@

inputPanel(
  sliderInput("rho_1", label = "initial plant cover:",
              min = 0.0, max = 1, value = 0.9, step = 0.01)
  )

@@

@@

# running the ode-solver
ODE_spex <- ode(y = ini_rho(input$rho_1), func = odesys_spex, times = 1.1^(1:50), parms = parms)

# transfer into ouput and calculate missing rho values
ODE_spex <- as.data.frame(ODE_spex )

par(mar = c(4,4,1,3)+0.1)
plot(rho_1 ~ time , data = ODE_spex , type = "l", ylim = c(0,1))
axis(4, at = round(tail(ODE_spex,1)$rho_1,2),cex.axis = 0.7, las = 1 )

>>>>

defparms <- list(
    m = 0.05,
    r = 1,
    b = 0.7, 
    K = 0.9, 
    a = 0.6,
    h = 50,
    L = 4, 
    alpha = 0,
    q = 0,
    c = 0,
    f = 0,
    v = 0,
    p = 0
  )
```

@@

inputPanel(
  sliderInput("r", label = "max. growth rate:",
              min = 0.0, max = 3, value = defparms$r, step = 0.01),
  sliderInput("b", label = "environmental quality:",
              min = 0.0, max = 1, value =   defparms$b, step = 0.01),
  sliderInput("K", label = "carrying capacity:",
              min = 0.0, max = 1, value =  defparms$K, step = 0.01),
  sliderInput("alpha", label = "water runoff:",
              min = 0.0, max = 1, value =  defparms$alpha, step = 0.01),
  sliderInput("f", label = "local facilitation:",
              min = 0.0, max = 1, value =  defparms$f, step = 0.01),
  sliderInput("c", label = "local competition:",
              min = 0.0, max = 1, value =  defparms$c, step = 0.01)
)

@@

inputPanel(
  sliderInput("m", label = "intrinsic mortality:",
              min = 0.0, max = 1, value =  defparms$m, step = 0.01),
  sliderInput("a", label = "search efficiency:",
              min = 0.0, max = 1, value =  defparms$a, step = 0.01), 
  sliderInput("h", label = "handling time:",
              min = 0.0, max = 200, value =  defparms$h, step = 1), 
  sliderInput("L", label = "livestock units:",
              min = 0.0, max = 100, value =  defparms$L, step = 1),
  sliderInput("q", label = "hill coefficient:",
              min = 0.0, max = 1, value =  defparms$q, step = 0.01),
  sliderInput("v", label = "local attractivity:",
              min = 0.0, max = 1, value =  defparms$v, step = 0.01),
  sliderInput("p", label = "local protection:",
              min = 0.0, max = 5, value =  defparms$p, step = 0.01)
)

@@

inputPanel(
  selectInput("gradient", label = "select gradient:",             choices = c("b", "L"), selected = "b")
  )

@@

source("../code/simfunctions.r")

  rho <- seq(0,1,length = 100)

@@

 par(mfrow = c(1,2))

  attractor(parms, localvals = TRUE, rho_1_ini = seq(0,1, length = 21), rho_11_ini = seq(0,1, length = 11))

 if(input$gradient == "b") bifurcation(parms, "b", c(0,1))
 if(input$gradient == "L") bifurcation(parms, "L", c(0,12))
